What do incoming university students believe about open science practices in

### 2021-05-11 analysis/Manuscript.Rmd
Restoring code for Jen

## The replication crisis
Interestingly, the vast majority of participants had not heard of "the replication crisis" <!-- add numeric estimate-->.

>>>>

## The replication crisis
Interestingly, only (`r round(sum(df$crisis==1, na.rm = TRUE)/length(df$crisis)*100, 0)`% ) of participants had heard of "the replication crisis", with (`r round(sum(df$crisis==2, na.rm = TRUE)/length(df$crisis)*100, 0)`% indicating that they had not heard of the crisis and %  ) <!-- add numeric estimate-->.
